\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2020-03-11 paper/main.tex
updated description of random analysis

Prior work in humans and animals has shown that the spatial profile of the local
field potential differs by frequency band~\citep[e.g., with respect to volume
conductance properties and contribution to the local field
potential;][]{BuzsEtal12, FrieEtal07, CronEtal11}.  For example, lower frequency
components of the local field potential tend to have higher power and extend
further in space than high-frequency components~\citep[e.g., ][]{MillEtal07,
MannEtal09}.  We wondered whether the reconstructions we observed might be
differently weighting or considering the contributions of activity at different
frequency bands.  We therefore examined a range of frequency bands ($\delta$:
2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$: 12--30 Hz; $\gamma_L$:
30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of broadband (BB)
power. We used second-order Butterworth bandpass filters to compute the activity
patterns within each narrow frequency band.  We defined broadband power as the
mean height of a linear robust regression fit in log-log space to the order 4
Morelet wavelet-computed power spectrum at 50 log-spaced frequencies from from
2--100 Hz~\citep{MannEtal09}. We then repeated our within-subject and
across-subject cross-validated reconstruction accuracy tests (analogous to
Fig.~\ref{fig:corrmap}) separately for each frequency band
(Fig.~\ref{fig:frequency}). (We also carried out a similar analysis on the
Hilbert transform-computed spectral power within each narrow band; see
Fig.~\freqpower.) Across both datasets, we found that our approach is best at
reconstructing patterns of broadband activity (right-most bars in
Figs.~\ref{fig:frequency}A and D), a correlate of population firing
rate~\citep{MannEtal09}.  We also achieved good reconstruction accuracy within
each narrow frequency band (Figs.~\ref{fig:frequency} and \freqpower).  Activity
at lower frequencies ($\delta$, $\theta$, $\alpha$, and $\beta$) tended to be
reconstructed better than high-frequency patterns ($\gamma_L$ and $\gamma_H$),
with reconstruction accuracy peaking in the $\alpha$ band.  Overall, these
results indicate that our approach is able to accurately recover information
within the 2--100 Hz range.

>>>>

Prior work in humans and animals has shown that the spatial profile of the local
field potential differs by frequency band~\citep[e.g., with respect to volume
conductance properties and contribution to the local field
potential;][]{BuzsEtal12, FrieEtal07, CronEtal11}.  For example, lower frequency
components of the local field potential tend to have higher power and extend
further in space than high-frequency components~\citep[e.g., ][]{MillEtal07,
MannEtal09}.  We wondered whether the reconstructions we observed might be
differently weighting or considering the contributions of activity at different
frequency bands.  We therefore examined a range of frequency bands ($\delta$:
2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$: 12--30 Hz; $\gamma_L$:
30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of broadband (BB)
power. We used second-order Butterworth bandpass filters to compute the activity
patterns within each narrow frequency band.  We defined broadband power as the
mean height of a linear robust regression fit in log-log space to the order 4
Morelet wavelet-computed power spectrum at 50 log-spaced frequencies from from
2--100 Hz~\citep{MannEtal09}. We then repeated our within-subject and
across-subject cross-validated reconstruction accuracy tests (analogous to
Fig.~\ref{fig:corrmap}) separately for each frequency band
(Fig.~\ref{fig:frequency}). (We also carried out a similar analysis on the
Hilbert transform-computed spectral power within each narrow band; see
Fig.~\freqpower.) Across both datasets, we found that our approach is best at
reconstructing patterns of broadband activity (right-most bars in
Figs.~\ref{fig:frequency}A and D), a correlate of population firing
rate~\citep{MannEtal09}.  We also achieved good reconstruction accuracy within
each narrow frequency band (Figs.~\ref{fig:frequency} and \freqpower).  Activity
at lower frequencies ($\delta$, $\theta$, $\alpha$, and $\beta$) tended to be
reconstructed better than high-frequency patterns ($\gamma_L$ and $\gamma_H$),
with reconstruction accuracy peaking in the $\theta$ band.  Overall, these
results indicate that our approach is able to accurately recover information
within the 2--100 Hz range.

### 2020-03-11 paper/supporting_information.tex
minor spellchecking and formatting
updated description of random analysis

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
%\doublespacing

@@

%JRM STOPPED HERE
\begin{figure}[p]
\centering \includegraphics[width=\textwidth]{figs/supplemental_7}
\caption{\textbf{Temporal stability of estimated patient-specific correlation
matrices.}  For each patient $s$, we computed their patient-specific correlation
matrix ($C_s$) using two different subsets of their recorded data.  We
correlated the upper triangles of these estimates of $C_s$ to obtain a single
correlation for each participant, reflecting how stable (in time) the estimates
were.  We computed this stability measure, for each patient, as a function of
how much data was used to estimate each $C_s$ (expressed as a proportion of the
patient's total dataset, as in Panels \textbf{A} and \textbf{C}; or as the total duration of the
patient's recordings, as in Panels \textbf{B} and \textbf{D}).  We also varied how the timepoints
that went into each estimate were related. Specifically, we first concatenated the data from each patient's recording sessions to
construct a single data timeseries (ignoring session boundaries) for each patient.  We then constructed two
estimates of $C_s$ by drawing each patient's data from two equally sized sets of timepoints chosen from their multi-session data matrix.
The timepoints were drawn either at \textit{random} without replacement (teal lines); from equally sized timespans at the start and end of the multi-session data matrix (\textit{apart}, blue lines); or from two equally sized timespans just prior to and just after the data midpoint (\textit{close}, purple lines).  Panels A and B display the resulting correlations for Dataset 1, and panels C and D display the correlations for Dataset 2.
Error ribbons in all panels denote 95\% confidence intervals (computed across patients).}
\label{fig:supplemental_7}
\end{figure}

\begin{figure}[p]
\centering \includegraphics[width=\textwidth]{figs/supplemental_8}
\caption{\textbf{Stability of full-brain correlation matrices across patients.}
We estimated full-brain correlation matrices ($\bar{K}$) using different subsets
of patients from each dataset. We explored how stable these estimates were as a
function of how many patients were used to compute $\bar{K}$. For each sample
size $n$ (number of patients), we drew two non-overlapping sets of $n$ patients
(without replacement) from the full set of patients in each dataset. We then estimated $\bar{K}$ using the two sets of $n$ patients.  We computed the correlation between the upper triangles of these matrices as a measure of how similar the matrices were.  We repeated this procedure 500 times for each value of $n$ (ranging from 1 up to $\frac{1}{2}$ of the total number of patients in the given dataset); this yielded a distribution of correlation coefficients for each value of $n$.  Panels \textbf{A} and \textbf{C} diplay the mean correlations as a function of $n$ for Datasets 1 and 2, respectively.  The error ribbons denote 95\% confidence intervals (computed across iterations).  Panels \textbf{B} and \textbf{D} display
the standard error of the mean (SEM) of these distributions of correlations as a function of $n$, for Datasets 1 and 2, respectively.  The error ribbons
denote bootstrap-derived 95\% confidence intervals.}
\label{fig:supplemental_8}
\end{figure}

\clearpage
\newpage
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}
\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}
% \newpage
% \renewcommand{\refname}{Supplemental references}
% \bibliography{memlab}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
%\doublespacing

@@

%JRM STOPPED HERE
\begin{figure}[p]
\centering \includegraphics[width=\textwidth]{figs/supplemental_7}
\caption{\textbf{Temporal stability of estimated patient-specific
    correlation matrices.}  For each patient $s$, we computed their
  patient-specific correlation matrix ($C_s$) using two different
  subsets of their recorded data.  We correlated the upper triangles
  of these estimates of $C_s$ to obtain a single correlation for each
  participant, reflecting how stable (in time) the estimates were.  We
  computed this stability measure, for each patient, as a function of
  how much data was used to estimate each $C_s$ (expressed as a
  proportion of the patient's total dataset, as in Panels \textbf{A}
  and \textbf{C}; or as the total duration of the patient's
  recordings, as in Panels \textbf{B} and \textbf{D}).  We also varied
  how the timepoints that went into each estimate were
  related. Specifically, we first concatenated the data from each
  patient's recording sessions to construct a single data timeseries
  (ignoring session boundaries) for each patient.  We then constructed
  two estimates of $C_s$ by drawing each patient's data from two
  equally sized sets of $t$ timepoints chosen from their multi-session
  data matrix.  These timepoints were drawn either at \textit{random}
  without replacement (teal lines); from equally sized timespans at
  the start and end of the multi-session data matrix (\textit{apart},
  blue lines); or from two equally sized timespans just prior to and
  just after the data midpoint (\textit{close}, purple lines).  For
  the random condition of this analysis, as we increased $t$, we
  ensured that all of the timepoints included in the analysis for
  smaller values of $t$ were also included in the analyses for larger
  values of $t$.  For example, the randomly drawn timepoints for
  $t = 2000$ included the same timepoints drawn for $t = 1000$, plus
  an additional 1000 new timepoints.  Panels A and B display the
  resulting correlations for Dataset 1, and panels C and D display the
  correlations for Dataset 2.  Error ribbons in all panels denote 95\%
  confidence intervals (computed across patients).}
\label{fig:supplemental_7}
\end{figure}

\begin{figure}[p]
\centering \includegraphics[width=\textwidth]{figs/supplemental_8}
\caption{\textbf{Stability of full-brain correlation matrices across
    patients.}  We estimated full-brain correlation matrices
  ($\bar{K}$) using different subsets of patients from each
  dataset. We explored how stable these estimates were as a function
  of how many patients were used to compute $\bar{K}$. For each sample
  size $n$ (number of patients), we drew two non-overlapping sets of
  $n$ patients (without replacement) from the full set of patients in
  each dataset. We then estimated $\bar{K}$ using the two sets of $n$
  patients.  We computed the correlation between the upper triangles
  of these matrices as a measure of how similar the matrices were.  We
  repeated this procedure 500 times for each value of $n$ (ranging
  from 1 up to $\frac{1}{2}$ of the total number of patients in the
  given dataset); this yielded a distribution of correlation
  coefficients for each value of $n$.  Panels \textbf{A} and
  \textbf{C} display the mean correlations as a function of $n$ for
  Datasets 1 and 2, respectively.  The error ribbons denote 95\%
  confidence intervals (computed across iterations).  Panels
  \textbf{B} and \textbf{D} display the standard error of the mean
  (SEM) of these distributions of correlations as a function of $n$,
  for Datasets 1 and 2, respectively.  The error ribbons denote
  bootstrap-derived 95\% confidence intervals.}
\label{fig:supplemental_8}
\end{figure}

\clearpage
\newpage
\renewcommand{\refname}{Supplemental references}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}
\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}
% \newpage

% \bibliography{memlab}
